\Title

### 2020-12-09 manuscript/manuscript.tex
Start a revision of the inversion section
Make some tweaks to the notation, including using B and m instead of Â
and ĉ since ^ is often used to denote an estimate. Removed some of the
^2 from the lambdas in the least-squares solutions. Removed the part
about Cholesky decomposition because that is used to solve the linear
system, not minimize the goal function (and not always, it depends on
what sklearn does). Added an ^o to the data in the equations to
distinguish between predicted and observed data.

\subsection{Fitting source coefficients}
\label{sec:eql-inversion}

Solving equations~\ref{eq:linear-problem-g} and~\ref{eq:linear-problem} is
equivalent to performing an inversion and thus solving an ill-posed problem by
nature due to the non-uniqueness and the instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions
(\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).

We can obtain the values of the source coefficients $\mathbf{c}$ that better
reproduce the measured field by minimizing an objective or misfit function
$\phi(\mathbf{c})$ through a least squares method:

\begin{equation}
    \phi(\mathbf{c}) =
        \left\lVert
            \mathbf{d} - \mathbf{A}\mathbf{c}
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
    \label{eq:misfit-unscaled}
\end{equation}

\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
and $\lambda_d$ is a \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term of the equation applies a zeroth-order Tikhonov
\citep{tikhonov1977} regularization to stabilize the solution.

In order to simplify the choice of the \emph{damping} parameter we scale the
Jacobian matrix so each column has unit variance.
We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
standard deviation of each column of the Jacobian matrix $\mathbf{A}$:

\begin{equation}
    \mathbf{S} =
    \begin{bmatrix}
        \sigma_1 & \cdots &0 \\
        \vdots & \ddots & \vdots \\
        0 & \cdots & \sigma_M
    \end{bmatrix}
    ,
\end{equation}

\noindent so equation~\ref{eq:linear-problem} can be written as:

\begin{equation}
    \mathbf{d}
    =
    \mathbf{A} \mathbf{S}\inv \mathbf{S} \mathbf{c}
    =
    \left[
        \mathbf{A} \mathbf{S}\inv
    \right]
    \left[
        \mathbf{S} \mathbf{c}
    \right]
    =
    \hat{\mathbf{A}} \hat{\mathbf{c}}
\end{equation}

\noindent where $\hat{\mathbf{A}}$ is the scaled Jacobian matrix and
$\hat{\mathbf{c}}$ is a vector containing scaled coefficients.

The misfit function defined on equation~\ref{eq:misfit-unscaled} can be then
rewritten as follows:

\begin{equation}
    \phi(\hat{\mathbf{c}}) =
        \left\lVert \mathbf{d}
        - \hat{\mathbf{A}}\hat{\mathbf{c}} \right\rVert ^ 2
        + \lambda \left\lVert \hat{\mathbf{c}} \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

\noindent where now $\lambda$ is a \emph{dimensionless} damping parameter.

Misfit function from equation~\ref{eq:misfit} is minimized through Cholesky
decomposition.
If the number of observation points is equal or larger to the number of
sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
well- or over-determined, respectively. Therefore, the scaled coefficients that
minimize the misfit function can be obtained through \citep{menke1989}:

\begin{equation}
    \hat{\mathbf{c}} =
        \left[
            \hat{\mathbf{A}}^\text{T} \hat{\mathbf{A}}
            + \lambda^2 \mathbf{I}
        \right]\inv
        \hat{\mathbf{A}}^\text{T}
        \mathbf{d}.
\end{equation}

@@

\begin{equation}
    \hat{\mathbf{c}} =
    \hat{\mathbf{A}}^\text{T}
        \left[
            \hat{\mathbf{A}} \hat{\mathbf{A}}^\text{T}
            + \lambda^2 \mathbf{I}
        \right]\inv
        \mathbf{d}.
\end{equation}

Once the scaled coefficients are obtained, the sources' coefficients
$\mathbf{c}$ can be obtained by rescaling
$\hat{\mathbf{c}}$:

\begin{equation}
    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{c}}.
\end{equation}

@@

\section{Performance of gradient boosted equivalent sources}

Our second goal is to assess the accuracy of the predictions achieved by the
gradient boosting algorithm while registering its performance by comparison
with the non-boosted equivalent sources.

We applied the gradient boosted equivalent sources to interpolate the synthetic
airborne survey on the same points of the target grid.
We selected several window sizes to assess how accuracy and performance depend
on that variable.
For each window size we gridded the synthetic data with different sets of
parameters. Then we compared each prediction to the target grid in order to get
the best prediction for each window size.
On every interpolation, block-averaged sources with relative depth are used
with a spacing of
\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}, and an
overlap of 50\% between adjacent windows.

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients.

Compare RMS with the one achieved by the best prediction carried out by the
non-boosted equivalent sources with block-averaged sources (see
Table~\ref{tab:parameters-airborne-survey}).
Calculated the fitting time relative to the time needed by non-boosted
equivalent sources.

\subsection{Overlapping}

Another factor that plays an important role on the accuracy of the predictions
and impacts the computation time needed to fit the source coefficients is the
amount of overlap between adjacent windows.
The previous choice of 50\% showed to be sufficiently good to achieve
acceptable accuracy, although a deeper study should be carried out to assess
how the amount of overlap impacts both accuracy and fitting time.

We interpolated the synthetic airborne survey using the gradient boosted
equivalent sources on the same points of the target grid.
The interpolations were carried out using different amount of overlap, from
0\% to 0.95\% with a step size of 0.05\%.
For each overlap, we gridded the synthetic data with different sets of
parameters, fixing the window size to INSERT-WINDOW-SIZE and using
block-averaged sources with relative depth and a spacing of
\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}.
We registered the RMS achieved by the best prediction for each overlap and the
computation time needed to fit the source coefficients.

\section{Gridding Australia gravity data}

>>>>

\subsection{Damped least-squares solution}
\label{sec:eql-inversion}

We can obtain the values of the source coefficients $\mathbf{c}$ that best
fit the observed field values $\mathbf{d}^o$ by minimizing the goal function

\begin{equation}
    \phi(\mathbf{c}) =
        \left\lVert
            \mathbf{d}^o - \mathbf{A}\mathbf{c}
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
    \label{eq:misfit-unscaled}
\end{equation}

\noindent where $\left\lVert \cdot \right\rVert$ symbolizes the L$_2$ norm and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.

The range of acceptable values for the damping parameter $\lambda_d$ will
depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
Consequently, this range will vary (often dramatically) between datasets,
making it difficult to choose an appropriate value for $\lambda_d$ in practice.

To solve this issue, we first scale the Jacobian matrix so that its elements
are unitless and each column has unit variance.
We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
standard deviation of each column of $\mathbf{A}$:

\begin{equation}
    \mathbf{S} =
    \begin{bmatrix}
        \sigma_1 & \cdots &0 \\
        \vdots & \ddots & \vdots \\
        0 & \cdots & \sigma_M
    \end{bmatrix}
    .
\end{equation}

We then write the forward problem in equation~\ref{eq:linear-problem} as

\begin{equation}
    \mathbf{d}
    =
    \mathbf{A} \mathbf{S}\inv \mathbf{S} \mathbf{c}
    =
    \left[
        \mathbf{A} \mathbf{S}\inv
    \right]
    \left[
        \mathbf{S} \mathbf{c}
    \right]
    =
    \mathbf{B} \mathbf{m}
\end{equation}

\noindent where $\mathbf{B}$ is the scaled and unitless Jacobian matrix and
$\mathbf{m}$ is a vector containing scaled coefficients with the same units as
the data.

The misfit function defined on equation~\ref{eq:misfit-unscaled} can be
rewritten as

\begin{equation}
    \phi(\mathbf{m}) =
        \left\lVert \mathbf{d}^o
        - \mathbf{B}\mathbf{m} \right\rVert ^ 2
        + \lambda \left\lVert \mathbf{m} \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.

If the number of observation points is equal or larger to the number of
sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
well- or over-determined, respectively. Therefore, the scaled coefficients that
minimize the misfit function can be obtained through \citep{menke1989}:

\begin{equation}
    \hat{\mathbf{m}} =
        \left[
            \mathbf{B}^\text{T} \mathbf{B}
            + \lambda \mathbf{I}
        \right]\inv
        \mathbf{B}^\text{T}
        \mathbf{d}^o.
\end{equation}

@@

\begin{equation}
    \hat{\mathbf{m}} =
    \mathbf{B}^\text{T}
        \left[
            \mathbf{B} \mathbf{B}^\text{T}
            + \lambda \mathbf{I}
        \right]\inv
        \mathbf{d}^o.
\end{equation}

Once the scaled coefficients are obtained, the coefficients
$\mathbf{c}$ can be obtained by

\begin{equation}
    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{m}}.
\end{equation}

@@
